Classless Java

### 2016-03-22 OOPSLA16/sections/Implementation.tex
Limitations.

\subsection{Limitations}\marco{ to reorganize with updated limitations}
Our prototype implementation using Lombok has certain limitations:
\begin{itemize}
\item The prototype does not support separate compilation yet. Currently all
  related interfaces have to appear in a single Java file. Therefore, changes to
  a single interface would require re-compiling the whole file. This compilation
  limitation is not caused by our algorithm. It is a Lombok implementation related
  issue: in Lombok it is hard to capture a type declaration from its reference,
  even harder when the type declaration is in other files (we have not found a
  way to do this yet).
\item At this stage our implementation only realizes the Eclipse handler and our
  experiments are all conducted in Eclipse. The implementation for
  \texttt{javac} is missing.
\item The current implementation does not take type-parameters into
  consideration, thus it does not support generics yet.
\end{itemize}

>>>>

\subsection{Limitations}\marco{ to reorganize with updated limitations}
\haoyuan{Should we only present the separate compilation and simple generics features in this (limitation) section?}
Our prototype implementation using Lombok has certain limitations:
\begin{itemize}
\item \haoyuan{The annotation \mixin does not support separate compilation yet. Using \mixin, all
  related interfaces have to appear in a single Java file. Therefore, changes to
  a single interface would require re-compiling the whole file. Nevertheless, to support separate compilation we
  studied an existing yet experimental feature \lstinline{@Delegate}, reused the name and modified its behavior.
  Now files in the same package can be compiled and \lstinline{@Delegate} has the same behavior as \mixin. A limitation is
  that users need to put references to the super types of the annotated type together with the annotation, for instance,
  \lstinline{@Delegate(types = Point2D.class)}. Another limitation is the methods generated by \lstinline{@Delegate} will
  not be visible in the Outline window, but they can still be auto-completed in Eclipse.}
\item At this stage our implementation only realizes the Eclipse handler and our
  experiments are all conducted in Eclipse. The implementation for
  \texttt{javac} is missing.
\item \haoyuan{The current implementation only supports simple generics, which means type parameters can be used, however, the generic
method typing is neither formalized in this paper nor implemented, but delegated to the Java compiler.}
\end{itemize}
